%\addcontentsline{toc}{chapter}{Hivatkozások}

\begin{thebibliography}{99}



\bibitem{AmbrosettiProdi} \textbf{Ambrosetti, A.; Prodi, G.}:  \textit{A Primer of Nonlinear Analysis}, Cambridge University Press,  1993.

\bibitem{ChowHale} {\bf  Chow, S.~N.;  Hale, J.~K.:}  {\em Methods of bifurcation theory}, Pitman
      Grundlehren der mathematischen Wissenschaften, 251, Springer, Berlin etc., 1996.

\bibitem{Farkas} {\bf  Farkas, M.:}  {\em Periodic Motions}, Berlin, Heidelberg and New York: Springer-Verlag, 1994.

\bibitem{HirzebruchScharlau} \textbf{Hirzebruch, F.; Scharlau, W.}:  \textit{Einführung in die Funktionalanalysis}, B.I.-Wissenschaftsverlag,  1971.

\bibitem{KolmogorovFomin} \textbf{Kolmogorov, A. N.; Fomin, Sz. V.}:  \textit{A függvényelmélet és a funkcionálanalízis elemei}, Mûszaki Könyvkiadó, Budapest,  1981.

\bibitem{Kovacs}{\bf Kovács, S.}: {\it Funkcionálanalízis feladatokban, egyetemi jegyzet}, Budapest, 2013.\\ ISBN: 978-963-284-445-9%\\
%(\url{http://numanal.inf.elte.hu/~alex/hu/anyag/PROGINF/FunkAnal/FunkAnalKS.pdf})

\bibitem{Kovacs2}{\bf Kovács, S.}: {\it Abstract bifurcations}, Mikl\'os Farkas Seminar on Applied Analysis, Budapest University of Technology, 22 February 2018.


\bibitem{ChebysevTau} {\bf Liefvendahl, M.}: {\it A Chebyshev Tau Spectral Method for the Calculation of Eigenvalues and Pseudospectra}, Technical Report, TRITA-NA-0125, KTH, Stockholm, 2001.

\bibitem{MarxVogt} \textbf{Marx, B.; Vogt, W.}:  \textit{Dynamische Systeme - Theorie und Numerik}, Spektrum,  2011.

\bibitem{MeiseVogt} \textbf{Meise, R.; Vogt, D.}:  \textit{Einführung in die Funktionalanalysis}, Vieweg,  1992.

\bibitem{PelczynskiSudakov} {\bf Pelczynski, A.; Sudakov, V. N.}: {\it Remark on noncomplemented
subspaces of the space$ m(S)$}, Colloq. Math. {\bf 9}  (1962), 85--88.

\bibitem{Poetzsch} \textbf{P\"otzsche, C.:} \emph{Bifurcation theory},  Lecture Notes, SS 2010, TU M\"unchen, 2011.


\bibitem{RodriguezAbernathy} {\bf Rodriguez, J.; Kobylus Abernathy, Kristen}: {\it On the solvability of nonlinear boundary value problems}, Differential Equations and Applications {\bf 1}(2)  (2010), 487--499.

\bibitem{multipoint} {\bf Rodriguez, J.; Taylor, P.}: {\it Multipoint boundary value problems for nonlinear ordinary differential equations}, Nonlinear Anal. {\bf 68}(11)  (2008), 3465--3474.


\bibitem{Simon} \textbf{Simon, P.}:  \textit{A funkcionálanalízis alapjai}, ELTE Eötvös Kiadó,  2017.

\bibitem{LSNum} {\bf Trif, D.}: {\it The Lyapunov-Schmidt method for two-point boundary value problems}, Fixed Point Theory {\bf 6}(1)  (2005), 119--132.

\bibitem{LISC} {\bf Trif, D.}: {\it LISC - A Matlab package for linear differential problems}, Romai Journal {\bf 1}  (2006), 203--208.

\bibitem{Werner} \textbf{Werner, D.}:  \textit{Funktionalanalysis}, Springer,  2011.

\bibitem{Whitley} {\bf Whitley, R. J.}: {\it Projecting $m$ onto $\mathfrak{c}_0$}, Amer. Math. Monthly {\bf 73}  (1966), 285--286.

\bibitem{Zeidler} \textbf{Zeidler, E.}:  \textit{Nonlinear Functional Analysis and its Applications I.}, Springer,  1986.
\end{thebibliography}





